Emulation of high multiplicity matrix elements for electron-positron and hadron-hadron colliders

### 2022-10-07 intro.tex
wrote: colour-ordered and one-loop factorisation
wrote: antenna functions
wrote: monte carlo

    \begin{figure}\label{fig:qcd_feynman_rules}
        \includegraphics[width=\linewidth]{introduction/qcd_feynman_rules.pdf}
        \caption{QCD Feynman rules.}
    \end{figure}

@@

    For a review of PDFs and how they are determined
    see Ref. \cite{Ethier:2020way,Jimenez-Delgado:2013sma}.
    In practice, these PDF fits are accessed through the
    LHAPDF interface \cite{Buckley:2014ana} which provides
    PDF sets from multiple working groups \cite{PDF4LHCWorkingGroup:2022cjn,Hou:2019efy,Bailey:2020ooq,NNPDF:2021njg}.
    The evolution of PDFs between factorisation scales is possible
    through the use of the Dokshitzer-Gribov-Lipatov-Altarelli-Parisi (DGLAP)
    equations \cite{Dokshitzer:1977sg,Gribov:1972ri,Lipatov:1974qm,Altarelli:1977zs}.
    \begin{equation}\label{eqn:DGLAP}
        \mu_{F}^{2} \dfrac{\partial}{\partial \mu_{F}^{2}}
        \begin{pmatrix}
            f_{q/h}(x,\mu_{F}) \\
            f_{g/h}(x,\mu_{F})
        \end{pmatrix} \\
        = \dfrac{\alpha_{s}(\mu_{F})}{2\pi} \int_{x}^{1} \dfrac{\mathrm{d}z}{z}
        \begin{pmatrix}
            P_{qq}(\frac{x}{z}) & P_{qg}(\frac{x}{z}) \\
            P_{gq}(\frac{x}{z}) & P_{gg}(\frac{x}{z})
        \end{pmatrix}
        \begin{pmatrix}
            f_{q/h}(x,\mu_{F}) \\
            f_{g/h}(x,\mu_{F})
        \end{pmatrix} \, ,
    \end{equation}
    where $P_{ba}(\dfrac{x}{z})$ are splitting functions
    representing parton $b$ emitting a parton $a$ carrying
    a momentum fraction $z$. These splitting functions are calculable
    as a power series in $\alpha_{s}$ where they have been computed
    up to three-loops \cite{Moch:2004pa,Vogt:2004mw}.
    At leading order \cite{Altarelli:1977zs} they are
    \begin{align}\label{eqn:AP_kernels}
        P^{(0)}_{qq}(z) &= C_{F}\left[\dfrac{1+z^{2}}{(1-z)_{+}} + \dfrac{3}{2}\delta(1-z)\right] \\
        P^{(0)}_{qg}(z) &= T_{R}\left[z^{2} + (1-z)^{2}\right] \\
        P^{(0)}_{gq}(z) &= C_{F}\left[\dfrac{1+(1-z)^{2}}{z^{2}}\right] \\
        P^{(0)}_{gg}(z) &= 2C_{A}\left[\dfrac{z}{(1-z)_{+}}+\dfrac{1-z}{z}+z(1-z)\right] + \left(\dfrac{11C_{A}-4T_{R}n_{f}}{6}\right)\delta(1-z)
    \end{align}
    where the `$+$'-prescription has been used to regulate divergences
    at $z = 1$.
    \begin{equation}\label{eqn:plus_prescription}
        \int_{0}^{1} \mathrm{d}z \; [g(z)]_{+}f(z) = \int_{0}^{1}\mathrm{d}z \; g(z)(f(z)-f(1)) \, ,
    \end{equation}
    where the function $f(z)$ cancels the divergence if it is
    sufficiently smooth at $z=1$.
    At leading order, there is a physical interpretation
    of the splitting kernels as the probability of finding a parton
    $a$ in parton $b$ carrying a fraction $x$ of the parent parton.

@@

    $\hat{\sigma}_{ab \rightarrow n}(Q, \mu_{F}, \mu_{R})$
    is the partonic cross-section which descibes the interaction of
    partons $a$ and $b$ scattering into $n$ particles,
    where the scattering occurs at energy scale $Q$,
    which is often taken to the $\hat{s}$.
    Notice that the partonic cross-section depends on
    both the factorisation scale, $\mu_{F}$ and
    the renormalisation scale, $\mu_{R}$
    (see \ref{chapter:qcd}).
    {\color{red} Need to mention how these scales
    are unphysical but there is a residual dependence
    on them at fixed-order calculations. Scale
    variations are a conventional way to determine
    the effects of higher order terms.
    Renormalisation will be discussed in Chapter 2
    when divergences are introduced.}

@@

\section{Scattering amplitudes and cross-sections}\label{sec:xs}
    As mentioned in the previous section, at
    collider experiments we typically collide
    two beams, consisting of bundles of energetic
    particles, and analyse the resulting products
    of these collisions. The predictions we make
    from our theoretical model are the partonic
    cross-sections. To arrive at an expression
    for the partonic cross-section, we need to
    first consider the hard scattering of particles.
    To model the hard collisions in
    a collider experiment, we look at the specific
    case of two particles colliding into $n$ particles.
    Scattering amplitudes are used to mathematically
    describe these scattering processes.
    For an initial-state
    $|i\rangle$ and final-state $|f\rangle$
    the scattering amplitude can be written as
    \begin{equation}\label{eqn:scattering}
        \langle f | S | i \rangle \, ,
    \end{equation}
    where the scattering matrix, or $S$-matrix
    can be decomposed into an identity matrix
    and a transfer matrix $\mathcal{T}$,
    \begin{equation}\label{eqn:S_matrix}
        S = \mathbbm{1} + \mathrm{i}\mathcal{T} \, .
    \end{equation}
    The $S$-matrix encodes all the information
    about how the initial-state will evolve
    into the final-state over time. By writing
    the $S$-matrix in this way, all the interactions
    are separated into the transfer matrix $\mathcal{T}$,
    as the identity matrix describes the free theory.
    By imposing a momentum conserving constraint
    on the $S$-matrix, the matrix element,
    $\mathcal{M}$, is defined in the following expression
    \begin{equation}\label{eqn:matrix_element}
        \langle f | \mathcal{T} | i \rangle = (2\pi)^{4} \delta^{4}\left(p_{a} + p_{b} - \sum_{f=1}^{n} p_{f}^{\mu}\right) \mathcal{M} \, ,
    \end{equation}
    where we take $p_{a}$ and $p_{b}$ to be
    the momenta of the two colliding
    particles in the initial-state, and $p_{f}$ to be the
    momenta of the $n$-particle final states.
    The transition probability of this scattering process
    is the modulus squared of the scattering amplitude
    \begin{equation}\label{eqn:S_prob}
        P = |\langle f | S | i \rangle|^{2} \propto | \langle f | \mathcal{M} | i \rangle |^{2}
    \end{equation}
    where $|\langle f | \mathcal{M} | i \rangle|^{2}  \equiv |\mathcal{M}|^{2}$
    is the matrix element squared \footnote{from henceforth we refer to the matrix
    element squared as matrix element}.

@@

    With the introduction of matrix elements and
    cross-sections complete, we will move the discussion onto
    Monte Carlo event generators. These event
    generators are multipurpose tools that
    incorporate many aspects of the theory discussed
    so far (and to be discussed) for practical use.
    Most importantly, they are
    used to compare theoretical predictions to
    experimental measurements.

\section{Monte Carlo event generator overview}
\subsection{Event unweighting}
\begin{itemize}
    \item MC generators are the main tools that
    people use to compare with experimental data.
    There are many groups that have their own tool.
    \item The usage of MC tools came about because
    the multi-dimensional phase-space integrals
    are too complex to do analytically.
    \item This doesn't mean that they only do
    the integrals, the event generators basically
    contain all the tools from phase-space generation
    to matrix element evaluation, to parton showers
    to hadronisation.
    \item Have a look at Katherina thesis to see
    how much I can skip because only really want to
    introduce unweighting. Probably along the lines
    of event weight is statistically sampled vs
    what they measure in real life. Therefore we need
    to unweight events.
\end{itemize}
\end{document}

>>>>

    \begin{figure}
        \includegraphics[width=\linewidth]{introduction/qcd_feynman_rules.pdf}
        \caption{QCD Feynman rules.}
        \label{fig:qcd_feynman_rules}
    \end{figure}

@@

    For a review of PDFs and how they are determined
    see Ref. \cite{Ethier:2020way,Jimenez-Delgado:2013sma}.
    In practice, these PDF fits are accessed through the
    LHAPDF interface \cite{Buckley:2014ana} which provides
    PDF sets from multiple working groups \cite{PDF4LHCWorkingGroup:2022cjn,Hou:2019efy,Bailey:2020ooq,NNPDF:2021njg}.
    The evolution of PDFs between factorisation scales is possible
    through the use of the Dokshitzer-Gribov-Lipatov-Altarelli-Parisi (DGLAP)
    equations \cite{Dokshitzer:1977sg,Gribov:1972ri,Lipatov:1974qm,Altarelli:1977zs}.
    \begin{equation}\label{eqn:DGLAP}
        \mu_{F}^{2} \dfrac{\partial}{\partial \mu_{F}^{2}}
        \begin{pmatrix}
            f_{q/h}(x,\mu_{F}) \\
            f_{g/h}(x,\mu_{F})
        \end{pmatrix} \\
        = \dfrac{\alpha_{s}(\mu_{F})}{2\pi} \int_{x}^{1} \dfrac{\mathrm{d}z}{z}
        \begin{pmatrix}
            P_{qq}(\frac{x}{z}) & P_{qg}(\frac{x}{z}) \\
            P_{gq}(\frac{x}{z}) & P_{gg}(\frac{x}{z})
        \end{pmatrix}
        \begin{pmatrix}
            f_{q/h}(x,\mu_{F}) \\
            f_{g/h}(x,\mu_{F})
        \end{pmatrix} \, ,
    \end{equation}
    where $P_{ba}(\frac{x}{z})$ are splitting functions
    representing parton $b$ emitting a parton $a$ carrying
    a momentum fraction $z$. These splitting functions are calculable
    as a power series in $\alpha_{s}$ where they have been computed
    up to three-loops \cite{Moch:2004pa,Vogt:2004mw}.
    At leading order \cite{Altarelli:1977zs} they are
    \begin{align}\label{eqn:AP_kernels}
        P^{(0)}_{qq}(z) &= C_{F}\left[\dfrac{1+z^{2}}{(1-z)_{+}} + \dfrac{3}{2}\delta(1-z)\right] \\
        P^{(0)}_{qg}(z) &= T_{R}\left[z^{2} + (1-z)^{2}\right] \\
        P^{(0)}_{gq}(z) &= C_{F}\left[\dfrac{1+(1-z)^{2}}{z^{2}}\right] \\
        P^{(0)}_{gg}(z) &= 2C_{A}\left[\dfrac{z}{(1-z)_{+}}+\dfrac{1-z}{z}+z(1-z)\right] + \left(\dfrac{11C_{A}-4T_{R}n_{f}}{6}\right)\delta(1-z)
    \end{align}
    where the `$+$'-prescription has been used to regulate divergences
    at $z = 1$.
    \begin{equation}\label{eqn:plus_prescription}
        \int_{0}^{1} \mathrm{d}z \; [g(z)]_{+}f(z) = \int_{0}^{1}\mathrm{d}z \; g(z)(f(z)-f(1)) \, ,
    \end{equation}
    where the function $f(z)$ cancels the divergence if it is
    sufficiently smooth at $z=1$.
    At leading order, there is a physical interpretation
    of the splitting kernels as the probability of finding a parton
    $a$ in parton $b$ carrying a fraction $x$ of the parent parton.

@@

    $\hat{\sigma}_{ab \rightarrow n}(Q, \mu_{F}, \mu_{R})$
    is the partonic cross-section which descibes the interaction of
    partons $a$ and $b$ scattering into $n$ particles,
    where the scattering occurs at energy scale $Q$,
    which is often taken to the $\hat{s}$.
    Notice that the partonic cross-section depends on
    both the factorisation scale, $\mu_{F}$ and
    the renormalisation scale, $\mu_{R}$
    (see Section~\ref{sec:renormalisation}). This will
    be discussed in Section~\ref{sec:scale_variations}
    in the context of theoretical uncertainties.

@@

\section{Scattering amplitudes and cross-sections}\label{sec:xs}
    As mentioned in the previous section, at
    collider experiments we typically collide
    two beams, consisting of bundles of energetic
    particles, and analyse the resulting products
    of these collisions. The predictions we make
    from our theoretical model are the partonic
    cross-sections. To arrive at an expression
    for the partonic cross-section, we need to
    first consider the hard scattering of particles.
    To model the hard collisions in
    a collider experiment, we look at the specific
    case of two particles colliding into $n$ particles.
    Scattering amplitudes are used to mathematically
    describe these scattering processes.
    For an initial-state
    $|i\rangle$ and final-state $|f\rangle$
    the scattering amplitude can be written as
    \begin{equation}\label{eqn:scattering}
        \langle f | S | i \rangle \, ,
    \end{equation}
    where the scattering matrix, or $S$-matrix
    can be decomposed into an identity matrix
    and a transfer matrix $\mathcal{T}$,
    \begin{equation}\label{eqn:S_matrix}
        S = \mathbbm{1} + \mathrm{i}\mathcal{T} \, .
    \end{equation}
    The $S$-matrix encodes all the information
    about how the initial-state will evolve
    into the final-state over time. By writing
    the $S$-matrix in this way, all the interactions
    are separated into the transfer matrix $\mathcal{T}$,
    as the identity matrix describes the free theory.
    By imposing a momentum conserving constraint
    on the $S$-matrix, the matrix element,
    $\mathcal{M}$, is defined in the following expression
    \begin{equation}\label{eqn:S_matrix_element}
        \langle f | \mathcal{T} | i \rangle = (2\pi)^{4} \delta^{4}\left(p_{a} + p_{b} - \sum_{f=1}^{n} p_{f}^{\mu}\right) \mathcal{M} \, ,
    \end{equation}
    where we take $p_{a}$ and $p_{b}$ to be
    the momenta of the two colliding
    particles in the initial-state, and $p_{f}$ to be the
    momenta of the $n$-particle final states.
    The transition probability of this scattering process
    is the modulus squared of the scattering amplitude
    \begin{equation}\label{eqn:S_prob}
        P = |\langle f | S | i \rangle|^{2} \propto | \langle f | \mathcal{M} | i \rangle |^{2}
    \end{equation}
    where $|\langle f | \mathcal{M} | i \rangle|^{2}  \equiv |\mathcal{M}|^{2}$
    is the matrix element squared \footnote{from henceforth we refer to the matrix
    element squared as matrix element}.

@@

    With the introduction of matrix elements and
    cross-sections complete, we will move the discussion onto
    more practical aspects of computations within the
    QCD framework. More specifically, we will discuss
    the divergent structure of matrix elements
    and the machinery developed to tackle these
    unphysical singularities.

\end{document}

### 2022-10-07 qcd.tex
wrote: monte carlo

@@

    \subsection{Quark-gluon antenna functions}
    \subsubsection{Three-parton tree-level antenna function}
    \begin{equation}\label{eqn:D30}
        \begin{split}
        D_{3}^{0}(1_{q},3_{g},4_{g}) = \dfrac{1}{s_{134}^{2}}&\left(\dfrac{2s_{134}^{2}s_{14}}{s_{13}s_{34}} + \dfrac{2s_{134}^{2}s_{13}}{s_{14}s_{34}} + \dfrac{s_{14}s_{34}+s_{34}^{2}}{s_{13}}\right. \\
        & \left. + \dfrac{s_{13}s_{34}+s_{34}^{2}}{s_{14}} + \dfrac{2s_{13}s_{14}}{s_{34}} + 5s_{134} + s_{34}\right) + \mathcal{O}(\epsilon) \, .
        \end{split}
    \end{equation}
    \subsubsection{Three-parton one-loop antenna functions}
    \begin{align}\label{eqn:D31}
        \mathcal{P}oles\left(D_{3}^{1}(1_{q},3_{g},4_{g})\right) =& \; 2\left(\mathbf{I}_{qg}^{(1)}(\epsilon, s_{13}) + \mathbf{I}_{qg}^{(1)}(\epsilon, s_{14}) + \mathbf{I}_{gg}^{(1)}(\epsilon, s_{34}) \right. \nonumber \\
        &\left. \quad -2\mathbf{I}_{qg}^{(1)}(\epsilon, s_{134}) \vphantom{\mathbf{I}_{gg}^{(1)}} \right) D_{3}^{0}(1_{q},3_{g},4_{g}) \, , \\
        \mathcal{F}inite\left(D_{3}^{1}(1_{q},3_{g},4_{g})\right) =& \; -\left(R(y_{13},y_{34})+R(y_{14},y_{34})+R(y_{13},y_{14}) + \dfrac{5}{3}\log{y_{13}}\nonumber \right. \\
        &\left. \vphantom{\dfrac{1}{1}} \quad + \dfrac{5}{3}\log{y_{14}} + \dfrac{11}{6}\log{y_{34}}\right) D_{3}^{0}(1_{q},3_{g},4_{g}) + \dfrac{1}{3s_{34}} \, .
    \end{align}

    \subsection{Gluon-gluon antenna functions}
    \subsubsection{Three-parton tree-level antenna function}
    \begin{align}\label{eqn:F30}
        F_{3}^{0}(3_{g},4_{g},5_{g}) =& \; \dfrac{2}{s_{345}^{2}}\left(\dfrac{s_{345}^{2}s_{34}}{s_{35}s_{45}} + \dfrac{s_{345}^{2}s_{35}}{s_{34}s_{45}} + \dfrac{s_{345}^{2}s_{45}}{s_{34}s_{35}} \right. \nonumber \\
        &\left. \vphantom{\dfrac{s_{345}^{2}s_{34}}{s_{35}s_{45}}} \quad \quad +\dfrac{s_{34}s_{35}}{s_{45}} + \dfrac{s_{34}s_{45}}{s_{35}} + \dfrac{s_{35}s_{45}}{s_{34}} + 4s_{345} + \mathcal{O}(\epsilon) \right) \, .
    \end{align}
    \subsubsection{Three-parton one-loop antenna functions}
    \begin{align}\label{eqn:F31}
        \mathcal{P}oles\left(F_{3}^{1}(3_{g},4_{g},5_{g})\right) =& \; 2\left(\mathbf{I}_{gg}^{(1)}(\epsilon,s_{34}) + \mathbf{I}_{gg}^{(1)}(\epsilon,s_{35}) + \mathbf{I}_{gg}^{(1)}(\epsilon,s_{45}) \right. \nonumber \\
        &\left. \quad -2\mathbf{I}_{gg}^{(1)}(\epsilon,s_{345})
        \right) F_{3}^{0}(3_{g},4_{g},5_{g}) \, , \\
        \mathcal{F}inite\left(F_{3}^{1}(3_{g},4_{g},5_{g})\right) =& -\left(R(y_{34},y_{35}) + R(y_{35},y_{45}) + R(y_{34},y_{45}) \vphantom{\dfrac{1}{1}} \right. \nonumber \\
        &\left. \quad + \, \dfrac{11}{6}\log{y_{34}} + \dfrac{11}{6}\log{y_{35}} + \dfrac{11}{6}\log{y_{45}} \right) F_{3}^{0}(3_{g},4_{g},5_{g}) \nonumber \\
        & \quad + \dfrac{1}{3s_{34}} + \dfrac{1}{3s_{35}} + \dfrac{1}{3s_{45}} + \dfrac{1}{3s_{345}} \, .
    \end{align}
\end{document}

>>>>

    Below we list the antenna functions relevant
    for multijet production in electron-positron
    annihiliation with a single quark flavour,
    namely the partonic channel $e^{-}e^{+} \rightarrow
    q \bar{q}$ + $ng$.
    For this we require the $A$, $D$, and $F$ antenna functions,
    see Table~\ref{table:antenna_functions}.
    The $i,j,k$ indices will be fixed such that $q = 1$, $\bar{q} = 2$,
    and $g \in \{3, 4, 5\}$ in view of using the
    antenna functions in a calculation where the momenta
    of partons will have fixed indices in a phase-space
    point.

    It will be useful to define the $\mathcal{P}oles$
    and $\mathcal{F}inite$ operators to extract the
    singular and finite contributions from an antenna
    function. However, there are still finite terms
    from the $\mathcal{P}oles$ operator coming from
    the IR singularity operators (cite here). Therefore,
    care has to be taken to extract all the finite
    remainders from the antenna functions.

    For the one-loop antenna functions, there are three
    different functions corresponding to the: leading colour,
    subleading colour, and closed quark look contributions.
    It is sufficient to consider the leading colour
    structure in this thesis as the remaining contributions
    are subleading. Ignoring subleading terms in
    colour is equivalent to taking the large $N_{c}$
    limit. For QCD where $N_{c} = 3$, neglecting
    subleading colour terms amounts to an
    approximately 10\% effect.

@@

    \subsection{Quark-antiquark antenna functions}
    The quark-antiquark antenna functions are derived by normalising
    the colour-ordered QCD radiative corrections to $\gamma^{*} \rightarrow q \bar{q}$
    at NNLO.
    \subsubsection{Three-parton tree-level antenna function}
    \begin{equation}\label{eqn:A30}
        A_{3}^{0}(1_{q}, 3_{g}, 2_{\bar{q}}) = \dfrac{1}{s_{123}}\left(\dfrac{s_{13}}{s_{23}} + \dfrac{s_{23}}{s_{13}} + 2\dfrac{s_{12}s_{123}}{s_{13}s_{23}}\right) + \mathcal{O}(\epsilon)
    \end{equation}

    \subsubsection{Three-parton one-loop antenna function}
    \begin{align}\label{eqn:A31}
        \mathcal{P}oles\left(A_{3}^{1}(1_{q}, 3_{g}, 2_{\bar{q}})\right) =& \; 2\left(\mathbf{I}_{qg}^{(1)}(\epsilon, s_{13}) + \mathbf{I}_{qg}^{(1)}(\epsilon, s_{23}) \right. \nonumber \\
        &\quad \left. -\mathbf{I}_{q\bar{q}}^{(1)}(\epsilon,s_{123})\right)A_{3}^{0}(1_{q},3_{g},2_{\bar{q}}) \, , \\
        \mathcal{F}inite\left(A_{3}^{1}(1_{q}, 3_{g}, 2_{\bar{q}})\right) =& -\left(R(y_{13}, y_{23}) + \dfrac{5}{3}\log{y_{13}}+\dfrac{5}{3}\log{y_{23}}\right)A_{3}^{0}(1_{q}, 3_{g}, 2_{\bar{q}}) \nonumber\\
        &\quad +\dfrac{1}{s_{123}} + \dfrac{s_{12}+s_{23}}{2s_{123}s_{13}} + \dfrac{s_{12}+s_{13}}{2s_{123}s_{23}} \nonumber \\
        &\quad -\dfrac{s_{13}}{2s_{123}(s_{12}+s_{13})}-\dfrac{s_{23}}{2s_{123}(s_{12}+s_{23})} \nonumber \\
        &\quad +\dfrac{\log{y_{13}}}{s_{123}}\left(2-\dfrac{1}{2}\dfrac{s_{13}s_{23}}{(s_{12}+s_{23})^{2}} + 2\dfrac{s_{13}-s_{23}}{s_{12}+s_{23}}\right) \nonumber  \\
        &\quad +\dfrac{\log{y_{23}}}{s_{123}}\left(2-\dfrac{1}{2}\dfrac{s_{13}s_{23}}{(s_{12}+s_{13})^{2}} + 2\dfrac{s_{23}-s_{13}}{s_{12}+s_{13}}\right) \, .
    \end{align}

    \subsection{Quark-gluon antenna functions}
    The quark-gluon antenna functions are obtained by considering
    the QCD real radiation corrections in the process $\tilde{\chi} \rightarrow \tilde{g} g$.
    \subsubsection{Three-parton tree-level antenna function}
    \begin{equation}\label{eqn:D30}
        \begin{split}
        D_{3}^{0}(1_{q},3_{g},4_{g}) = \dfrac{1}{s_{134}^{2}}&\left(\dfrac{2s_{134}^{2}s_{14}}{s_{13}s_{34}} + \dfrac{2s_{134}^{2}s_{13}}{s_{14}s_{34}} + \dfrac{s_{14}s_{34}+s_{34}^{2}}{s_{13}}\right. \\
        & \left. + \dfrac{s_{13}s_{34}+s_{34}^{2}}{s_{14}} + \dfrac{2s_{13}s_{14}}{s_{34}} + 5s_{134} + s_{34}\right) + \mathcal{O}(\epsilon) \, .
        \end{split}
    \end{equation}
    \subsubsection{Three-parton one-loop antenna functions}
    \begin{align}\label{eqn:D31}
        \mathcal{P}oles\left(D_{3}^{1}(1_{q},3_{g},4_{g})\right) =& \; 2\left(\mathbf{I}_{qg}^{(1)}(\epsilon, s_{13}) + \mathbf{I}_{qg}^{(1)}(\epsilon, s_{14}) + \mathbf{I}_{gg}^{(1)}(\epsilon, s_{34}) \right. \nonumber \\
        &\left. \quad -2\mathbf{I}_{qg}^{(1)}(\epsilon, s_{134}) \vphantom{\mathbf{I}_{gg}^{(1)}} \right) D_{3}^{0}(1_{q},3_{g},4_{g}) \, , \\
        \mathcal{F}inite\left(D_{3}^{1}(1_{q},3_{g},4_{g})\right) =& \; -\left(R(y_{13},y_{34})+R(y_{14},y_{34})+R(y_{13},y_{14}) + \dfrac{5}{3}\log{y_{13}}\nonumber \right. \\
        &\left. \vphantom{\dfrac{1}{1}} \quad + \dfrac{5}{3}\log{y_{14}} + \dfrac{11}{6}\log{y_{34}}\right) D_{3}^{0}(1_{q},3_{g},4_{g}) + \dfrac{1}{3s_{34}} \, .
    \end{align}

    \subsection{Gluon-gluon antenna functions}
    The gluon-gluon antenna functions are obtained from the
    QCD real radiation corrections in the process $H \rightarrow g g$.
    \subsubsection{Three-parton tree-level antenna function}
    \begin{align}\label{eqn:F30}
        F_{3}^{0}(3_{g},4_{g},5_{g}) =& \; \dfrac{2}{s_{345}^{2}}\left(\dfrac{s_{345}^{2}s_{34}}{s_{35}s_{45}} + \dfrac{s_{345}^{2}s_{35}}{s_{34}s_{45}} + \dfrac{s_{345}^{2}s_{45}}{s_{34}s_{35}} \right. \nonumber \\
        &\left. \vphantom{\dfrac{s_{345}^{2}s_{34}}{s_{35}s_{45}}} \quad \quad +\dfrac{s_{34}s_{35}}{s_{45}} + \dfrac{s_{34}s_{45}}{s_{35}} + \dfrac{s_{35}s_{45}}{s_{34}} + 4s_{345} + \mathcal{O}(\epsilon) \right) \, .
    \end{align}
    \subsubsection{Three-parton one-loop antenna functions}
    \begin{align}\label{eqn:F31}
        \mathcal{P}oles\left(F_{3}^{1}(3_{g},4_{g},5_{g})\right) =& \; 2\left(\mathbf{I}_{gg}^{(1)}(\epsilon,s_{34}) + \mathbf{I}_{gg}^{(1)}(\epsilon,s_{35}) + \mathbf{I}_{gg}^{(1)}(\epsilon,s_{45}) \right. \nonumber \\
        &\left. \quad -2\mathbf{I}_{gg}^{(1)}(\epsilon,s_{345})
        \right) F_{3}^{0}(3_{g},4_{g},5_{g}) \, , \\
        \mathcal{F}inite\left(F_{3}^{1}(3_{g},4_{g},5_{g})\right) =& -\left(R(y_{34},y_{35}) + R(y_{35},y_{45}) + R(y_{34},y_{45}) \vphantom{\dfrac{1}{1}} \right. \nonumber \\
        &\left. \quad + \, \dfrac{11}{6}\log{y_{34}} + \dfrac{11}{6}\log{y_{35}} + \dfrac{11}{6}\log{y_{45}} \right) F_{3}^{0}(3_{g},4_{g},5_{g}) \nonumber \\
        & \quad + \dfrac{1}{3s_{34}} + \dfrac{1}{3s_{35}} + \dfrac{1}{3s_{45}} + \dfrac{1}{3s_{345}} \, .
    \end{align}
    \subsection{Limiting behaviour of antenna functions}
    Examining (\ref{eqn:A30}) more closely, it becomes clear
    that the correct IR behaviour is exhibited by the antenna
    function. The first two terms correspond to the gluon
    going collinear with the quark and antiquark. The final
    term encapsulates singularity in the limit of the gluon
    going soft.

    The other antenna functions have similar limiting behaviour,
    collapsing to the single collinear and soft splitting functions
    in the relevant regions of phase-space.
\end{document}
